QPLIB: A Library of Quadratic Programming Instances

### 2018-02-08 QPLIB-2.2.tex
replace T by \top for transposition

When a $Q^i$ is positive semidefinite (PSD), i.e., the corresponding constraint/objective function is convex, general Hessians are in fact equivalent to diagonal ones. In particular, since every PSD matrix can be factorized as $Q^i = L^i (L^i)^T$, e.g.~by the (incomplete) Cholesky factorization, the term $\half x^T Q^i x \equiv \half \sum_{j \in \Mcn} z^{i\;2}_j$ where $z^{i\;T} = x^T L^i$. Hence, one might maintain that D** problems need not be distinguished from C** ones. However in reality, this is only true for ``complicated'' constraints but not for ``simple'' ones, because the above reformulation technique introduces additional linear constraints, $L^{i\;T} x - z^i = 0$. Indeed, while \textit{C*L} (and, a fortiori, \textit{C*}\{\textit{C},\textit{Q}\}) can always be brought to \textit{D*L} (\textit{D*}\{\textit{C},\textit{Q}\}), using the above technique \textit{C*B} becomes \textit{D*L}, which may be significantly different from \textit{D*B}. In practice, a diagonal convex objective function under linear constraints is found in many applications (e.g., \cite{FrFG16,FrGe06a,FrGe09a,FGGP11}), so that it still makes sense to distinguish the \textit{D*L} case where the objective function is ``naturally'' separable from that where separability is artificially introduced.

>>>>

When a $Q^i$ is positive semidefinite (PSD), i.e., the corresponding constraint/objective function is convex, general Hessians are in fact equivalent to diagonal ones. In particular, since every PSD matrix can be factorized as $Q^i = L^i (L^i)^\top$, e.g.~by the (incomplete) Cholesky factorization, the term $\half x^\top Q^i x \equiv \half \sum_{j \in \Mcn} z^{i\;2}_j$ where $z^{i\;\top} = x^\top L^i$. Hence, one might maintain that D** problems need not be distinguished from C** ones. However in reality, this is only true for ``complicated'' constraints but not for ``simple'' ones, because the above reformulation technique introduces additional linear constraints, $L^{i\;\top} x - z^i = 0$. Indeed, while \textit{C*L} (and, a fortiori, \textit{C*}\{\textit{C},\textit{Q}\}) can always be brought to \textit{D*L} (\textit{D*}\{\textit{C},\textit{Q}\}), using the above technique \textit{C*B} becomes \textit{D*L}, which may be significantly different from \textit{D*B}. In practice, a diagonal convex objective function under linear constraints is found in many applications (e.g., \cite{FrFG16,FrGe06a,FrGe09a,FGGP11}), so that it still makes sense to distinguish the \textit{D*L} case where the objective function is ``naturally'' separable from that where separability is artificially introduced.
